\begin{acknowledgements}

It is a significant stage of life to spend five years working on a PhD degree, and I am very grateful to have worked with wonderful people during this period. First and foremost, I would like to thank my advisor Trevor Darrell, for being a great mentor to introduce me into the wonderful field of academic research and to encourage me to explore new fields and research directions. I would also like to thank Tom Griffiths, Jitendra Malik, Alyosha Efros, and Bruno Olshausen, for high-level and interdisciplinary guidances allowing me to see beyond my otherwise limited research field.

I had never imagined a more enjoyable graduate school life before I joined Berkeley, and it is an honor to meet and work with fellow postdocs and graduate students: Oriol Vinyals, Jon Barron, Sergey Karayev, Trevor Owens, Hyun Oh Song, Ning Zhang, Judy Hoffman, Allie Janoch, Jon Long, Jeff Donahue, Evan Shelhamer, Joshua Abbott, Joseph Austerweil, Dave Golland, Matthieu Salzmann, Brian Kulis, Mario Fritz, Mario Christoudias, Ross Girshick, Sergio Guadarrama, and many others. Grad school has been unimaginably colorful with your company.

I appreciate my internship days at the NEC Labs America and Google Research. My thanks go to Chang Huang, Kai Yu, Mei Han, Thomas Leung, Alexander Toshev, and Sergey Ioffe, for offering the great opportunity for me to enlarge my vision, and to boldly go into the era of large-scale deep learning.

Last but not least, I am deeply indebted to the love, tolerance and support from my wife Sizhu and my parents. This thesis is dedicated to them with my sincere gratitude.

\end{acknowledgements}
